Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-08 article.tex
Make cfg example look ok

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.48\textwidth}
  \centering
  \begin{tikzpicture}
    \node [cbox, font=\ttfamily\tiny, align=left] (cfa) at (0,0) {define i32 @square(i32 \%0) \{\\1:\\\ \%2 = icmp sgt i32 \%0, 0\\\ br i1 \%2, label \%3, label \%9\ ; succs = \%3, \%9\\3:\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ; preds = \%1, \%3\\\ \%4 = phi i32 [ \%0, \%1 ], [ \%7, \%3 ]\\\ \%5 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ \%6 = add i32 \%5, \%0\\\ \%7 = sub i32 \%4, 1\\\ \%8 = icmp ugt i32 \%7, 0\\\ br i1 \%8, label \%3, label \%9\ ; succs = \%3, \%9\\9:\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ; preds = \%3, \%1\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10\\\}};
  \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
  \centering
  \begin{tikzpicture}
    \node [cbox, font=\ttfamily\tiny, align=left] (a) at (0,0) {1:\\\ \%2 = icmp sgt i32 \%0, 0\\\ br i1 \%2, label \%3, label \%9\ \ \ \ \ \ \ };
    \node [cbox, font=\ttfamily\tiny, align=left, below=0.5cm of a] (b) {3:\\\ \%4 = phi i32 [ \%0, \%1 ], [ \%7, \%3 ]\\\ \%5 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ \%6 = add i32 \%5, \%0\\\ \%7 = sub i32 \%4, 1\\\ \%8 = icmp ugt i32 \%7, 0\\\ br i1 \%8, label \%3, label \%9\\9:\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10\\\}};
    \node [cbox, font=\ttfamily\tiny, align=left, below=0.5cm of b] (c) {9:\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10};
    \node[right=2cm, invisible] (ab) at ($(a.south)!0.5!(b.north)$) {};
    \node[right=2cm, invisible] (bc) at ($(b.south)!0.5!(c.north)$) {};
  \draw [-latex] (a) -- (b);
  %\draw [-latex] (a) to[out=-15,in=15] (c);
  \draw [-latex] (b) -- (c);
  %\draw [-latex] (c.north) to[bend right=1000] (b.north);
  \draw  (a.south) to [in=0] (ab);
  \draw  (ab) to [in=0] (bc);
  \draw [-latex]  (bc) to [out=180,in=70] (c.north);
  \end{tikzpicture}
  \end{subfigure}
  \hfill
  \caption{Compiler phases, backend highlighted}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.48\textwidth}
  \centering
  \begin{tikzpicture}
    \node [cbox, font=\ttfamily\tiny, align=left] (cfa) at (0,0) {define i32 @square(i32 \%0) \{\\1:\\\ \%2 = icmp sgt i32 \%0, 0\\\ br i1 \%2, label \%3, label \%9\ ; succs = \%3, \%9\\3:\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ; preds = \%1, \%3\\\ \%4 = phi i32 [ \%0, \%1 ], [ \%7, \%3 ]\\\ \%5 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ \%6 = add i32 \%5, \%0\\\ \%7 = sub i32 \%4, 1\\\ \%8 = icmp ugt i32 \%7, 0\\\ br i1 \%8, label \%3, label \%9\ ; succs = \%3, \%9\\9:\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ ; preds = \%3, \%1\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10\\\}};
  \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{0.48\textwidth}
  \centering
  \begin{tikzpicture}
    \node [cbox, font=\ttfamily\tiny, align=left] (a) at (0,0) {1:\\\ \%2 = icmp sgt i32 \%0, 0\\\ br i1 \%2, label \%3, label \%9\ \ \ \ \ \ \ };
    \node [cbox, font=\ttfamily\tiny, align=left, below=0.5cm of a] (b) {3:\\\ \%4 = phi i32 [ \%0, \%1 ], [ \%7, \%3 ]\\\ \%5 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ \%6 = add i32 \%5, \%0\\\ \%7 = sub i32 \%4, 1\\\ \%8 = icmp ugt i32 \%7, 0\\\ br i1 \%8, label \%3, label \%9\\9:\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10\\\}};
    \node [cbox, font=\ttfamily\tiny, align=left, below=0.5cm of b] (c) {9:\\\ \%10 = phi i32 [ 0, \%1 ], [ \%6, \%3 ]\\\ ret i32 \%10};

    \node[right= 1cm of a.south, invisible] (ac1)  {};
    \node[below= 0.166667cm of ac1, invisible] (ac2)  {};
    \node[right= 1.333333cm of ac2, invisible] (ac3)  {};
    \node[right= 1cm of c.north, invisible] (ac6)  {};
    \node[above= 0.166667cm of ac6, invisible] (ac5)  {};
    \node[right= 1.333333cm of ac5, invisible] (ac4)  {};

    \node[right= 1cm of b.north, invisible] (bb1)  {};
    \node[above= 0.166667cm of bb1, invisible] (bb2)  {};
    \node[right= 1.166667cm of bb2, invisible] (bb3)  {};
    \node[right= 1cm of b.south, invisible] (bb6)  {};
    \node[below= 0.166667cm of bb6, invisible] (bb5)  {};
    \node[right= 1.166667cm of bb5, invisible] (bb4)  {};

    %\node[right=2.5cm of ab, invisible] (abr)  {};
    %\node[right=2.5cm of bc, invisible] (bcr)  {};
  \draw [-latex] (a) -- (b);
  %\draw [-latex] (a) to[out=-15,in=15] (c);
  \draw [-latex] (b) -- (c);

  \draw          (ac1.center) -- (ac2.center) -- (ac3.center) -- (ac4.center) -- (ac5.center);
  \draw [-latex] (ac5.center) -- (ac6.center);

  \draw          (bb2.center) -- (bb3.center) -- (bb4.center) -- (bb5.center) -- (bb6.center);
  \draw [-latex] (bb2.center) -- (bb1.center);
  %\draw [-latex] (c.north) to[bend right=1000] (b.north);
  %\draw  (a.south) to  (ab);
  %\draw  (ab) to  (abr);
  %\draw  (abr) to  (bcr);
  %\draw  (bcr) to  (bc);
  %\draw  (ab) to  (bc);
  %\draw [-latex]  (bc) to [out=180,in=70] (c.north);
  \end{tikzpicture}
  \end{subfigure}
  \hfill
  \caption{CFG of \lstinline!@square! of \lstinline!square.ll!} % FIXME: not entirely correct (square.ll is @main)
\end{figure}
